Submission and Formatting Instructions for MLSys 2024

### 2023-12-07 docs/mlsys2024template/example_paper.tex
add mlsys2024 example

% Use the following line for the initial blind version submitted for review:
% \usepackage{mlsys2024}

% If accepted, instead use the following line for the camera-ready submission:
\usepackage[accepted]{mlsys2024}

% The \mlsystitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\mlsystitlerunning{Step-by-Step: Training IMU-based Gestures with Live Feedback}

@@

\twocolumn[
\mlsystitle{Step-by-Step: Training IMU-based Gestures with Live Feedback}

@@

\begin{mlsysauthorlist}
\mlsysauthor{Michael Schnebly}{h}
\end{mlsysauthorlist}

\mlsysaffiliation{h}{School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, USA}

\mlsyscorrespondingauthor{Michael Schnebly}{michael\_schnebly@g.harvard.edu}

@@

\begin{abstract}
Recognizing user-defined gestures in IMU data unlocks new forms of creativity and accessibility in human-computer interaction. However, training gesture recognition models is a difficult task that requires a deep understanding of machine learning. We present Step-by-Step, a software tool that allows users to train gesture recognition models with live visual and auditory feedback. Step-by-Step is designed to be accessible to users with no machine learning experience, while providing a powerful codebase for advanced users. This work makes the following contributions: ...
% (1) a novel interface for training gesture recognition models with live feedback, (2) a novel interface for visualizing IMU data, and (3) a novel interface for visualizing gesture recognition models.
\end{abstract}
]

@@

\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
% \printAffiliationsAndNotice{\mlsysEqualContribution} % otherwise use the standard text.

>>>>

% Use the following line for the initial blind version submitted for review:
\usepackage{mlsys2024}

% If accepted, instead use the following line for the camera-ready submission:
% \usepackage[accepted]{mlsys2024}

% The \mlsystitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\mlsystitlerunning{Submission and Formatting Instructions for MLSys 2024}

@@

\twocolumn[
\mlsystitle{Submission and Formatting Instructions for MLSys 2024}

@@

\begin{mlsysauthorlist}
\mlsysauthor{Aeiau Zzzz}{equal,to}
\mlsysauthor{Bauiu C.~Yyyy}{equal,to,goo}
\mlsysauthor{Cieua Vvvvv}{goo}
\mlsysauthor{Iaesut Saoeu}{ed}
\mlsysauthor{Fiuea Rrrr}{to}
\mlsysauthor{Tateu H.~Yasehe}{ed,to,goo}
\mlsysauthor{Aaoeu Iasoh}{goo}
\mlsysauthor{Buiui Eueu}{ed}
\mlsysauthor{Aeuia Zzzz}{ed}
\mlsysauthor{Bieea C.~Yyyy}{to,goo}
\mlsysauthor{Teoau Xxxx}{ed}
\mlsysauthor{Eee Pppp}{ed}
\end{mlsysauthorlist}

\mlsysaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
\mlsysaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
\mlsysaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}

\mlsyscorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
\mlsyscorrespondingauthor{Eee Pppp}{ep@eden.co.uk}

@@

\begin{abstract}
This document provides a basic paper template and submission guidelines.
Abstracts must be a single paragraph, ideally between 4--6 sentences long.
Gross violations will trigger corrections at the camera-ready phase.
\end{abstract}
]

@@

%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
\printAffiliationsAndNotice{\mlsysEqualContribution} % otherwise use the standard text.
